\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-12 k-planar.tex
added comments

\note{DW}{I am pretty sure one can get treewidth 3 for $(g,1)$-planar graphs, combining \cref{framed} with the treewidth 3 result in \citep{DHHW}. I think the best place for this result is reference \citep{DHHW} (since the present paper pre-dates \citep{DHHW} and this addition will increase the significance of \citep{DHHW}). }

@@

\note{DW}{I am pretty sure one can get treewidth 3 here using \cref{framed} and the treewidth 3 result in \citep{DHHW}. I think the best place for this result is reference \citep{DHHW} (since the present paper pre-dates \citep{DHHW} and this addition will increase the significance of \citep{DHHW}).}

>>>>

\note{DW}{I am pretty sure one can get treewidth 3 for $(g,1)$-planar graphs, combining \cref{framed} with the treewidth 3 result in \citep{DHHW}. I think the best place for this result is reference \citep{DHHW} since the present paper pre-dates \citep{DHHW} (and this addition will increase the significance of \citep{DHHW}). }

@@

\note{DW}{I am pretty sure one can get treewidth 3 here using \cref{framed} and the treewidth 3 result in \citep{DHHW}. I think the best place for this result is reference \citep{DHHW} since the present paper pre-dates \citep{DHHW} (and this addition will increase the significance of \citep{DHHW}).}
